\section{Rationale for Application}
% the world has loads of information
% biomedical engineering is a rapidly growing and reaching into the public
%% sectors' interests
% information needs explaining
% I have a vocation as an educator
There are various reasons why involvement in this project would be beneficial.
Apart from the obvious personal development benefits,
Participating in this project would be a chance to give something back to
the community in a tangible way.
This new project is an opportunity for the new \url{physicsworld.com}
site to attract a broader audience, perhaps one that is educated, but is not
necessarily scientifically literate, but that have the curiosity to find out
about relevant topics in scientific fields. Playing a part in this project would
provide the opportunity to perform that service: give broader sectors of the
population a window to real scientific achievements, while remaining challenging
enough to write appealing content for scientists' interests.
\medskip\\In general, the generation, reception and sharing of information
about the world is growing. Scientific research in many fields is no longer a
far fetched entity, but its relevant topics are also becoming relevant to the
public domain. The handling of information and the accurate presentation of
scientific facts to the public has always been of great importance, however
that importance has increased in a world where content creation is as easily
achievable as content reception. The implications of a curious and well informed
audience range from basic social interactions to potential public policies
and even funding to the same research.
This ideal general audience starts with a platform that provides them with the
scientific context of the latest achievements; proving to be most
beneficial, and participating in it would be most rewarding.\medskip\\ The
field of biomedical engineering has become
increasingly relevant, due to advances in many fields: a clear example is in
immunohistochemistry, which combines many disciplines like medicine, biology,
physics, chemistry and computer science; all of which have been evolving at
growing rates.
Biomedical engineering's advancements pose important questions
that require ethical approval from governments and organisations,
and the future of the field involves even bigger questions, like
genetic manipulation, biorobotics and human enhancement, will certainly
be assessed by governments in the future, and having an informed population
would aid the decisions made by the electorate influence policies to be based
on scientific facts rather than private entities' economics
interests.\medskip\\ On a personal level, participating in this
project would enhance the tools of communication to accomodate different
audiences. It would also provide the participants with an enhanced experience
in writing at a professional level and thus allow them to aspire to more
renowed publications.
In some cases, the academic path involves scientists to restrict
themselves to teaching to focused audiences, not exploiting their knowlegde
to impact on different sectors. Previous teaching experience to undergraduate
students to social sciences have caused the realisation of a lack of
communication from scientists to a general audience; leading scientific
facts to be put to questioning or debate. This project would enable all
participants in the website's relaunch to colaborate and become efficient
and better educators in the field of biomedical engineering, both to their
peers, as well as to broader audiences.
